---
title: "idconv"
output: github_document
---

Wrapper functions to convert gene identifiers available from the org.Hs.eg.db bioconductor package.

# Installation  

```

devtools::install_github("uhlitz/idconv")

```

# Examples

```{r}

library(idconv)

# wrapper functions for specific identifiers:
SYMBOL_to_ENTREZID(c("EGR1", "FOS"))
ENTREZID_to_SYMBOL(c("1958", "2353"))
SYMBOL_to_ENSEMBL(c("EGR1", "FOS"))
ENSEMBL_to_SYMBOL(c("ENSG00000120738", "ENSG00000170345"))

# generalised functions:
IDX_to_IDY(ids = "NM_005252", from = "REFSEQ", to = "SYMBOL")

```

# Non-unique mappings

If more than one mapping is available, `AnnotationDbi` returns a warning (1:many mappings) and
`idconv` wrapper functions return NAs for target ids by default. 
If desired, wrapper functions in this package can be forced to return unique mappings.
Forcing unique mappings is however not recommended.

```{r}

# example for non-unique mapping:
SYMBOL_to_ENSEMBL("IER3")
SYMBOL_to_ENSEMBL("IER3", force_unique = T)

```
