---
title: "idconv"
output: github_document
---

Wrapper functions to convert gene identifiers available from the org.Hs.eg.db bioconductor package.

# Installation  

```

devtools::install_github("uhlitz/idconv")

```

# Examples

## Wrapper functions for specific identifiers:

You can choose from the following predefined functions:

`SYMBOL_to_ENTREZID()`, `ENTREZID_to_SYMBOL`, `SYMBOL_to_ENSEMBL`, `ENSEMBL_to_SYMBOL`,
`SYMBOL_to_REFSEQ`, `REFSEQ_to_SYMBOL`.


```{r}

library(idconv)
SYMBOL_to_ENTREZID(c("EGR1", "FOS"))
ENTREZID_to_SYMBOL(c("1958", "2353"))
SYMBOL_to_ENSEMBL(c("EGR1", "FOS"))
ENSEMBL_to_SYMBOL(c("ENSG00000120738", "ENSG00000170345"))

```

## Generic function

You can use the generic function to map other identifiers:

```{r}

IDX_to_IDY(ids = "NM_005252", from = "REFSEQ", to = "ENSEMBL")

```

Or simply define your own custom conversion function:

```{r}

REFSEQ_to_ENSEMBL <- function(ids) IDX_to_IDY(ids = ids, from = "REFSEQ", to = "ENSEMBL")
REFSEQ_to_ENSEMBL("NM_005252")

```

# Non-unique mappings

If more than one mapping is available, `AnnotationDbi` returns a warning (1:many mappings) and
`idconv` wrapper functions return concatenated target IDs by default. 
If desired, wrapper functions in this package can be forced to return unique mappings.
Forcing unique mappings is however not recommended.

```{r}

SYMBOL_to_ENSEMBL("IER3", force_unique = F) # default
SYMBOL_to_ENSEMBL("IER3", force_unique = NA)
SYMBOL_to_ENSEMBL("IER3", force_unique = T)

```

# Subtype IDs

When converting to RefSeq, a subtype for target IDs can be specified, eg. `NM` or `NP`:

```{r}

SYMBOL_to_REFSEQ("IER3", to_sub = "NM")
SYMBOL_to_REFSEQ("IER3", to_sub = "NP")

```
